---
title: "SizeBiasedSamplingPseudocode"
author: "Paul M"
date: "1/29/2021"
output: pdf_document
---

# Size-biased sampling via MCMC sampling

Let's define a distribution to try it on
```{r}
Exponential <- function(dRate,x){
	return (dRate*exp(-dRate*x))
}
```

We could just as easily use R's pre-defined exponential density function

Here's the pseudcode for Size-biased MCMC. We pass it the following arguments:
Density: the name of the function that defines our density
Param1: the parameter of the density function (we assume it has just one parameter)
NoOfIts: how many iterations to run
StepSize: at each iteration we will propose a move drawn from an unif[iStepSize,StepSize] rv 
LowRange: The low end of the interval over which we will sample
HighRange: The high end of the interval over which we will sample

```{r SBMCMC}
SizedBiasedMCMC <- function(Density, Param1,NoOfIts,StepSize,LowRange,HighRange){
	 #start somewhere
	 x <- runif(1,LowRange,HighRange)
	 Accepteds <- vector(mode="double",length=NoOfIts)
	 
	 # do Metropolis Algorithm
	 for (i in 1:NoOfIts){
	 	
	 	# propose new x - for example
	 	xprime <- x+runif(1,-StepSize,StepSize)
	 	
	 	# Check we haven't gone outside our range of interest
		if (xprime> HighRange)
			xprime <- HighRange-(xprime-HighRange) # this treats the edge of the range as a 'reflecting boundary'.
		if (xprime< LowRange)
			xprime <- LowRange-(xprime-LowRange) # this treats the edge of the range as a 'reflecting boundary'.

		# Calculate acceptance prob PAccept  <-  min{1,q(x'->x)f(x')/q(x->x')f(x)} ...... here f(y)=y*Density(param1,y) 
		# ADD CODE TO DO THAT HERE
		
    # Decide whether to move or not? 
		p <- runif(1)
		if (p<Paccept)
		{
			x <- xprime
		}
		# update the vector of states
		Accepteds[i] <- x
	 }
	hist(Accepteds,breaks=50)
	return (Accepteds)
}
```

Test the code using something like the following:
```{r}
SB <- SizedBiasedMCMC(Exponential,1,1500000,0.9,0,10)
HSB <- hist(SB,breaks=500)
plot(HSB$mids,HSB$density,pch='.',cex=3)
curve(x*exp(-x),add=TRUE,col="blue")
```
